\cvsection{Publications}

\vspace{-17mm}

\begin{cventries}
    \cventry
    {} % Empty position
    {\ } % Title
    {\ } % Empty location
    {} % Empty date
    {
        \begin{cvitemize2}
            \item \textbf{Jing Dai}, Jianbo Yuan, Yiwen Lu, Haohua Zhu, Sheng Yi, and Weixin Yan. ``IntuitCap: A 60-DOF Upper-body Motion Capture System for Dexterous Robot Manipulation''. Accepted by 8th The International Conference on Robotics, Control and Automation Engineering (RCAE), 2025.
            \item \textbf{Jing (Daisy) Dai*}, Qianshu Wang*, Shurui Zhang*, Bin Zhao, Jiahong Zhang, Jianbo Yuan, and Yiwen Lu. ``HOVER: Generalized Retargeting for Dexterous Manipulation''. To be presented at IROS 2025 Workshop on Learning from Human Teleoperation; \textit{In preparation for} Robotics: Science and Systems (RSS), 2026.
            \item Xinyue Xu*, Jieqiang Sun*, \textbf{Jing (Daisy) Dai*}, Siyuan Chen, Lanjie Ma, Ke Sun, Bin Zhao, Jianbo Yuan, and Yiwen Lu. ``DexCanvas: Bridging Human Demonstrations and Robot Learning for Dexterous Manipulation''. Submitted to International Conference on Learning Representations (ICLR), 2026.
            \item Jianbo Yuan, Haohua Zhu, \textbf{Jing Dai}, and Sheng Yi. ``Development of the Bioinspired Tendon-Driven DexHand 021 with Proprioceptive Compliance Control''. \textit{IEEE Robotics and Automation Letters (RA-L)}, 2025.
            \item Jianbo Yuan, \textbf{Jing Dai}, Yerui Fan, Yaxiong Wu, Yunpeng Liang, Weixin Yan. ``Robustness study of the bio-inspired musculoskeletal arm robot based on the data-driven iterative learning algorithm''. \textit{Science China Information Sciences}, 2025, 68: 222203. doi: 10.1007/s11432-024-4540-7
            \item Yuchen Jia, Suzhen Wu, Gang Wang, \textbf{Jing Dai}, Jingyuan Gao, Rui Lei, and Aonan Li. ``A Bionic Peacock'', \textit{Invention Patent}, ZL116423533A, 2023-07-14. \href{https://pss-system.cponline.cnipa.gov.cn/documents/detail?prevPageTit=changgui}{\textcolor{link}{[Link]}}
            % \vspace{-4mm}
        \end{cvitemize2}
    }
\end{cventries}
